Modelling last glacial cycle ice dynamics in the Alps

### 2018-07-31 articles/cycle/alps-cycle.tex
Update acknowledgements and data availability.

\codedataavailability{%
    PISM is available as open-source software at http://pism-docs.org/. Upon
    publication, we will be happy to make aggregated model output available
    through The Cryosphere. Please contact the corresponding author for more
    detailed model output data.}

\authorcontribution{%
    J.~Seguinot designed the study, ran the simulations, and wrote most of
    the manuscript. M.~Huss provided modern ice thickness data. All authors
    contributed to interpreting results and improving the text. The idea for
    this study stems in part from an excursion organised by F.~Preusser in the
    central Alps in 2012.}

\competinginterests{%
    We have no conflict of interest in publishing these results.}

@@

    This manuscript is partly based on a previous study on the Cordilleran Ice
    Sheet which is part of J.~Seguinot's PhD thesis. The experimental design
    used here, as well as the general layout of this study, are largely
    inspired by Irina Rogozhina and Arjen~P. Stroeven. We are very thankful to
    Constantine Khroulev, Ed Bueler, and Andy Aschwanden for providing constant
    help and development with PISM, in particular with recent issues with the
    computation of ice temperature (Github issue no.~371) and with the
    computation of bedrock deformation (Github issues no.~370 and 377). We are
    equally thankful to Giovanni Monegato and Marc Luetscher for very
    insightful discussions of preliminary model results during the European
    Geoscience Union General Assembly~2017. This work was supported by the
    Swiss National Foundation grant no.~200021-153179/1 to M.~Funk. Computer
    resources were provided by the Swiss National Supercomputing Centre (CSCS)
    allocation no.~s573 to J.~Seguinot.

>>>>

\codedataavailability{%
    PISM is available as open-source software at http://pism-docs.org/.
    Aggregated model output will be made available upon publication. Please
    contact the corresponding author for more detailed model output data.}

\authorcontribution{%
    J.~Seguinot designed the study, ran the simulations, and wrote most of
    the manuscript. All authors contributed to interpreting the results and
    improving the text. M.~Huss provided modern ice thickness data. The idea
    for this study stems in part from an excursion organised by F.~Preusser in
    the central Alps in 2012.}

\competinginterests{%
    The authors declare that they have no conflict of interest.}

@@

    We are very thankful to Constantine Khroulev, Ed Bueler, and Andy
    Aschwanden for providing constant help and development with PISM, in
    particular with recent issues with the computation of ice temperature
    (Github issue no.~371) and with the computation of bedrock deformation
    (Github issues no.~370 and 377). We are equally thankful to three
    anonymous reviewers and Giovanni Monagato for very constructive inputs
    during peer-review, and to Marc Luetscher for insightful discussions of
    preliminary results during the EGU~General Assembly~2017. The experimental
    design and article layout used here are based on previous work which
    received much guidance from Irina Rogozhina and Arjen~P. Stroeven.
    The current work was supported by the Swiss National Science Foundation
    grants no.~200020-169558 and 200021-153179/1 to M.~Funk. Computer resources
    were provided by the Swiss National Supercomputing Centre (CSCS)
    allocations no.~s573 and sm13 to J.~Seguinot.
